Title

### 2015-12-10 paper/paper.tex
added feature weights

\begin{table}[H]
\centering
\caption{Features used by subgraph partition scorer}
\label{tab:subgraph_selection_features}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Feature}                           & \textbf{Description}                            \\ \midrule
partition\_length                          & Number of groups in the partition               \\
partition\_length\_squared                 & Number of groups in the partition squared       \\
mean/min/max/std\_dev partition\_facts     & Number of facts per partition                   \\
mean/min/max/std\_dev subgraph\_similarity & Pairwise subgraph similarity between all groups \\
mean/min/max/std\_dev verb\_similarity     & Pairwise verb similarity between all groups     \\ \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[H]
\centering
\caption{Features used by subgraph partition scorer}
\label{tab:subgraph_selection_features}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Feature}                      & \textbf{Weight} \\ \midrule
\# groups in partition                & 10.29970016     \\
\# groups in partition squared        & -1.17590317     \\
mean \# facts per partition           & 1.09239105      \\
max \# facts per partition            & -0.21350766     \\
min \# facts per partition            & 0.11910551      \\
std\_dev \# facts per partition       & 0.20101274      \\
mean pairwise subgraph similarity     & -18.66465415    \\
min pairwise subgraph similarity      & 1.77360275      \\
max pairwise subgraph similarity      & -0.38517871     \\
std\_dev pairwise subgraph similarity & -7.56089457     \\
mean pairwise verb set similarity     & -1.02945557     \\
min pairwise verb set similarity      & 0.04030027      \\
max pairwise verb set similarity      & 0.89961397      \\
std\_dev pairwise verb set similarity & -0.17388411     \\ \bottomrule
\end{tabular}
\end{table}

\subsubsection{Test}

\begin{table}[H]
\centering
\caption{Evaluation Metrics for Subgraph Selection Classifier}
\label{tab:subgraph_selection_eval}
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Precision} & \textbf{Recall} & \textbf{f1-score} & \textbf{auc} & \textbf{support} \\ \midrule
0.93               & 0.93            & 0.93              & 0.98         & 428              \\ \bottomrule
\end{tabular}
\end{table}
